Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$ --- where $\cross_H(r^*)$, defined in \eqref{eqn:cross}, is the set of segments in $H$ crossing $r^*$ --- which is an instance of the find-all-sorted version of Problem $\mathscr{D}$. The following lemma, proven in Appendix~\ref{app:hv}, presents some crucial properties for these ``cross'' sets.

@@

>>>>

We pay particular attention to the sets $\cross_H(r^*)$ of the rectangles $r^*$ in $R^*_i$, where $\cross_H(r^*)$, defined in \eqref{eqn:cross}, is the set of segments in $H$ crossing $r^*$. The following lemma, proven in Appendix~\ref{app:hv}, presents some crucial properties for these sets.

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of the above lemma assures us that
